Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-07-05 nge.tex
Changed Agent in Pilot Agent and removed NGE's pilot
Forgot to save nge.tex

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{figures/rp_architecture_compact_atlaswms_paper.pdf}
   \vspace{-0.3in}
  \caption{NGE Architecture: The PilotManager and UnitManager reside on a DTN
  while the Agent is executed on a worker node. Color coding: gray for
  entities external to NGE\@; white for APIs; purple for NGE's modules; green
  for pilots; yellow for module's components.}
\label{fig:arch-overview}
\end{figure}

NGE exposes an API to describe workloads (Fig.~\ref{fig:arch-overview}, green
squares) and pilots (Fig.~\ref{fig:arch-overview}, red circles), and to
instantiate a PilotManager and a UnitManager. The PilotManager submits pilots
to Titan's PBS batch system via SAGA API (Fig.~\ref{fig:arch-overview}, dash
arrow). %, as done by PanDA Broker to submit MPI scripts. 
Once scheduled, the pilot's Agent is bootstrapped on a MOM node and the
Agent's Executors on the worker nodes.

The UnitManager and the Agent communicate via a database instantiated on a
DTN so as to be reachable by both modules. The UnitManager schedules units to
the Agent's Scheduler (Fig.~\ref{fig:arch-overview}, solid arrow) and the
Agent's Scheduler schedules the units on one or more Agent's Executor.
% for execution. The Agent's executors can manage one or more worker nodes,
% depending on performance evaluations.

The NGE Agent uses the Open Run-Time Environment (ORTE) for communication and
coordination of the execution of units. This environment is a critical
component of the OpenMPI implementation~\cite{castain05:_open_rte}.
%, cug-2016}.
ORTE is able to minimize the system overhead while submitting tasks by
avoiding filesystem bottlenecks and race conditions with network sockets.

>>>>

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{figures/rp_architecture_compact_atlaswms_paper.pdf}
   \vspace{-0.3in}
  \caption{NGE Architecture: The PilotManager and UnitManager reside on a DTN
  while the Pilot Agent is executed on a worker node. Color coding: gray for
  entities external to NGE\@; white for APIs; purple for NGE's modules; green
  for pilots; yellow for module's components.}
\label{fig:arch-overview}
\end{figure}

NGE exposes an API to describe workloads (Fig.~\ref{fig:arch-overview}, green
squares) and pilots (Fig.~\ref{fig:arch-overview}, red circles), and to
instantiate a PilotManager and a UnitManager. The PilotManager submits pilots
to Titan's PBS batch system via SAGA API (Fig.~\ref{fig:arch-overview}, dash
arrow). %, as done by PanDA Broker to submit MPI scripts. 
Once scheduled, the Pilot Agent is bootstrapped on a MOM node and the
Agent's Executors on the worker nodes.

The UnitManager and the Pilot Agent communicate via a database instantiated on a
DTN so as to be reachable by both modules. The UnitManager schedules units to
the Agent's Scheduler (Fig.~\ref{fig:arch-overview}, solid arrow) and the
Agent's Scheduler schedules the units on one or more Agent's Executor.
% for execution. The Agent's executors can manage one or more worker nodes,
% depending on performance evaluations.

The Pilot Agent uses the Open Run-Time Environment (ORTE) for communication and
coordination of the execution of units. This environment is a critical
component of the OpenMPI implementation~\cite{castain05:_open_rte}.
%, cug-2016}.
ORTE is able to minimize the system overhead while submitting tasks by
avoiding filesystem bottlenecks and race conditions with network sockets.
